### 2010-02-20 trunk/deliverables/D2_2_Ontology/classes.tex
common tag added
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@463 d8b0c59b-6544-0410-94d9-83a5658a058e
greatly extending conceptualisation part with UML diagrams, also updating to reflect changes in implementations
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@582 d8b0c59b-6544-0410-94d9-83a5658a058e

\subsubsection{Class: \texttt{fgo:Resource}}

@@

\textcolor{white}{\textbf{super\_class\_of}} & \htmlref{\texttt{fgo:ScreenFlow}}{subs:ScreenFlow}, \htmlref{\texttt{fgo:Screen}}{subs:Screen}, \htmlref{\texttt{fgo:FlowControlElement}}{subs:FlowControlElement}, \htmlref{\texttt{fgo:ScreenComponent}}{subs:ScreenComponent}, \htmlref{\texttt{fgo:Condition}}{subs:Condition}, \htmlref{\texttt{fgo:Fact}}{subs:Fact}, \htmlref{\texttt{fgo:WithPreConditions}}{subs:WithPreConditions}, \htmlref{\texttt{fgo:WithPostConditions}}{subs:WithPostConditions}, \htmlref{\texttt{fgo:WithConditions}}{subs:WithConditions}, \htmlref{\texttt{fgo:Precondition}}{subs:Precondition}, \htmlref{\texttt{fgo:Postcondition}}{subs:Postcondition}, \htmlref{\texttt{fgo:Pipe}}{subs:Pipe}, \htmlref{\texttt{fgo:Trigger}}{subs:Trigger} \\ \hline
\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:contains}}{subs:contains}, \htmlref{\texttt{fgo:hasIcon}}{subs:hasIcon}, \htmlref{\texttt{fgo:hasScreenshot}}{subs:hasScreenshot}, \htmlref{\texttt{fgo:hasTag}}{subs:hasTag}, \htmlref{\texttt{fgo:hasVersion}}{subs:hasVersion}, \htmlref{\texttt{fgo:hasId}}{subs:hasId}, \htmlref{\texttt{fgo:hasName}}{subs:hasName}, \htmlref{\texttt{fgo:hasType}}{subs:hasType}, \htmlref{\texttt{fgo:hasDefinition}}{subs:hasDefinition} \\ \hline

@@

\subsubsection{Class: \texttt{fgo:ScreenFlow}}
\subsubsection{Class: \texttt{fgo:Screen}}
\subsubsection{Class: \texttt{fgo:FlowControlElement}}
\textcolor{white}{\textbf{super\_class\_of}} & \htmlref{\texttt{fgo:ScreenFlowStart}}{subs:ScreenFlowStart}, \htmlref{\texttt{fgo:ScreenFlowEnd}}{subs:ScreenFlowEnd}, \htmlref{\texttt{fgo:Connector}}{subs:Connector} \\ \hline
\subsubsection{Class: \texttt{fgo:ScreenFlowStart}}
\subsubsection{Class: \texttt{fgo:ScreenFlowEnd}}
\subsubsection{Class: \texttt{fgo:Connector}}
\subsubsection{Class: \texttt{fgo:ScreenComponent}}
\textcolor{white}{\textbf{super\_class\_of}} & \htmlref{\texttt{fgo:Operator}}{subs:Operator}, \htmlref{\texttt{fgo:FormElement}}{subs:FormElement}, \htmlref{\texttt{fgo:BackendService}}{subs:BackendService} \\ \hline
\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:hasAction}}{subs:hasAction}, \htmlref{\texttt{fgo:hasTrigger}}{subs:hasTrigger}, \htmlref{\texttt{fgo:hasLibrary}}{subs:hasLibrary} \\ \hline
\subsubsection{Class: \texttt{fgo:Operator}}
\subsubsection{Class: \texttt{fgo:FormElement}}
\subsubsection{Class: \texttt{fgo:BackendService}}

@@

\subsubsection{Class: \texttt{fgo:Condition}}

@@

\textcolor{white}{\textbf{in\_range\_of}} & \htmlref{\texttt{fgo:hasPreCondition}}{subs:hasPreCondition}, \htmlref{\texttt{fgo:hasPostCondition}}{subs:hasPostCondition}, \htmlref{\texttt{fgo:hasCondition}}{subs:hasCondition} \\ \hline

@@

\subsubsection{Class: \texttt{fgo:Fact}}

@@

\subsubsection{Class: \texttt{fgo:WithPreConditions}}

@@

\textcolor{white}{\textbf{label}} & With-precondition \\ \hline
\textcolor{white}{\textbf{description}} & Those kinds of resource which can have pre-conditions 
    (i.e., screens and screen flows). \\ \hline

@@

\textcolor{white}{\textbf{unionOf}} & \htmlref{\texttt{fgo:ScreenFlow}}{subs:ScreenFlow}, \htmlref{\texttt{fgo:Screen}}{subs:Screen}, \htmlref{\texttt{fgo:Action}}{subs:Action} \\ \hline

@@

\subsubsection{Class: \texttt{fgo:WithPostConditions}}

@@

\textcolor{white}{\textbf{label}} & With-precondition \\ \hline
\textcolor{white}{\textbf{description}} & Those kinds of resource which can have pre-conditions 
    (i.e., screens and screen flows). \\ \hline
\textcolor{white}{\textbf{unionOf}} & \htmlref{\texttt{fgo:ScreenFlow}}{subs:ScreenFlow}, \htmlref{\texttt{fgo:Screen}}{subs:Screen}, \htmlref{\texttt{fgo:ScreenComponent}}{subs:ScreenComponent} \\ \hline

@@

\subsubsection{Class: \texttt{fgo:WithConditions}}

@@

\textcolor{white}{\textbf{unionOf}} & \htmlref{\texttt{fgo:WithPreConditions}}{subs:WithPreConditions}, \htmlref{\texttt{fgo:WithPostConditions}}{subs:WithPostConditions} \\ \hline

@@

\subsubsection{Class: \texttt{fgo:Action}}
\subsubsection{Class: \texttt{fgo:Library}}

@@

@@

\subsubsection{Class: \texttt{fgo:Precondition}}

@@

\subsubsection{Class: \texttt{fgo:Postcondition}}

@@

@@

\subsubsection{Class: \texttt{fgo:Definition}}
\subsubsection{Class: \texttt{fgo:ResourceReference}}

@@

\subsubsection{Class: \texttt{fgo:ScreenDefinition}}

@@

\subsubsection{Class: \texttt{fgo:Pipe}}

@@

\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:hasIdBBFrom}}{subs:hasIdBBFrom}, \htmlref{\texttt{fgo:hasIdConditionFrom}}{subs:hasIdConditionFrom}, \htmlref{\texttt{fgo:hasIdBBTo}}{subs:hasIdBBTo}, \htmlref{\texttt{fgo:hasIdConditionTo}}{subs:hasIdConditionTo}, \htmlref{\texttt{fgo:hasIdActionTo}}{subs:hasIdActionTo} \\ \hline

@@

\subsubsection{Class: \texttt{fgo:Trigger}}

@@

\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:hasIdBBFrom}}{subs:hasIdBBFrom}, \htmlref{\texttt{fgo:hasIdBBTo}}{subs:hasIdBBTo}, \htmlref{\texttt{fgo:hasIdActionTo}}{subs:hasIdActionTo}, \htmlref{\texttt{fgo:hasNameFrom}}{subs:hasNameFrom} \\ \hline

@@

\subsubsection{Class: \texttt{fgo:FormDefinition}}

@@

@@

\subsubsection{Class: \texttt{fgo:OperatorDefinition}}

@@

@@

\subsubsection{Class: \texttt{fgo:BackendServiceDefinition}}

@@

>>>>

\subsubsection*{Class: \texttt{fgo:Action}}

@@

@@

\subsubsection*{Class: \texttt{fgo:BackendService}}

@@

\subsubsection*{Class: \texttt{fgo:BackendServiceDefinition}}
\subsubsection*{Class: \texttt{fgo:Condition}}

@@

\textcolor{white}{\textbf{in\_range\_of}} & \htmlref{\texttt{fgo:hasCondition}}{subs:hasCondition}, \htmlref{\texttt{fgo:hasPostCondition}}{subs:hasPostCondition}, \htmlref{\texttt{fgo:hasPreCondition}}{subs:hasPreCondition} \\ \hline

@@

\subsubsection*{Class: \texttt{fgo:Connector}}
\subsubsection*{Class: \texttt{fgo:Definition}}
\subsubsection*{Class: \texttt{fgo:Fact}}

@@

\subsubsection*{Class: \texttt{fgo:FlowControlElement}}

@@

\textcolor{white}{\textbf{super\_class\_of}} & \htmlref{\texttt{fgo:Connector}}{subs:Connector}, \htmlref{\texttt{fgo:ScreenFlowEnd}}{subs:ScreenFlowEnd}, \htmlref{\texttt{fgo:ScreenFlowStart}}{subs:ScreenFlowStart} \\ \hline

@@

@@

\subsubsection*{Class: \texttt{fgo:FormDefinition}}

@@

@@

\subsubsection*{Class: \texttt{fgo:FormElement}}

@@

@@

\subsubsection*{Class: \texttt{fgo:Library}}

@@

\textcolor{white}{\textbf{description}} & Libraries are references to external code libraries required for the execution of a particular building block at runtime. \\ \hline

@@

\subsubsection*{Class: \texttt{fgo:Operator}}
\subsubsection*{Class: \texttt{fgo:OperatorDefinition}}
\subsubsection*{Class: \texttt{fgo:Pipe}}
\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:hasIdActionTo}}{subs:hasIdActionTo}, \htmlref{\texttt{fgo:hasIdBBFrom}}{subs:hasIdBBFrom}, \htmlref{\texttt{fgo:hasIdBBTo}}{subs:hasIdBBTo}, \htmlref{\texttt{fgo:hasIdConditionFrom}}{subs:hasIdConditionFrom}, \htmlref{\texttt{fgo:hasIdConditionTo}}{subs:hasIdConditionTo} \\ \hline
\subsubsection*{Class: \texttt{fgo:Postcondition}}
\subsubsection*{Class: \texttt{fgo:Precondition}}

@@

\subsubsection*{Class: \texttt{fgo:Resource}}

@@

\textcolor{white}{\textbf{super\_class\_of}} & \htmlref{\texttt{fgo:Condition}}{subs:Condition}, \htmlref{\texttt{fgo:Fact}}{subs:Fact}, \htmlref{\texttt{fgo:FlowControlElement}}{subs:FlowControlElement}, \htmlref{\texttt{fgo:Pipe}}{subs:Pipe}, \htmlref{\texttt{fgo:Postcondition}}{subs:Postcondition}, \htmlref{\texttt{fgo:Precondition}}{subs:Precondition}, \htmlref{\texttt{fgo:Screen}}{subs:Screen}, \htmlref{\texttt{fgo:ScreenComponent}}{subs:ScreenComponent}, \htmlref{\texttt{fgo:ScreenFlow}}{subs:ScreenFlow}, \htmlref{\texttt{fgo:Trigger}}{subs:Trigger}, \htmlref{\texttt{fgo:WithConditions}}{subs:WithConditions}, \htmlref{\texttt{fgo:WithPostConditions}}{subs:WithPostConditions}, \htmlref{\texttt{fgo:WithPreConditions}}{subs:WithPreConditions} \\ \hline
\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:contains}}{subs:contains}, \htmlref{\texttt{fgo:hasDefinition}}{subs:hasDefinition}, \htmlref{\texttt{fgo:hasIcon}}{subs:hasIcon}, \htmlref{\texttt{fgo:hasId}}{subs:hasId}, \htmlref{\texttt{fgo:hasName}}{subs:hasName}, \htmlref{\texttt{fgo:hasScreenshot}}{subs:hasScreenshot}, \htmlref{\texttt{fgo:hasTag}}{subs:hasTag}, \htmlref{\texttt{fgo:hasType}}{subs:hasType}, \htmlref{\texttt{fgo:hasVersion}}{subs:hasVersion} \\ \hline

@@

\subsubsection*{Class: \texttt{fgo:ResourceReference}}

@@

\subsubsection*{Class: \texttt{fgo:Screen}}
\subsubsection*{Class: \texttt{fgo:ScreenComponent}}
\textcolor{white}{\textbf{super\_class\_of}} & \htmlref{\texttt{fgo:BackendService}}{subs:BackendService}, \htmlref{\texttt{fgo:FormElement}}{subs:FormElement}, \htmlref{\texttt{fgo:Operator}}{subs:Operator} \\ \hline
\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:hasAction}}{subs:hasAction}, \htmlref{\texttt{fgo:hasLibrary}}{subs:hasLibrary}, \htmlref{\texttt{fgo:hasTrigger}}{subs:hasTrigger} \\ \hline
\subsubsection*{Class: \texttt{fgo:ScreenDefinition}}

@@

\subsubsection*{Class: \texttt{fgo:ScreenFlow}}

@@

@@

\subsubsection*{Class: \texttt{fgo:ScreenFlowEnd}}
\subsubsection*{Class: \texttt{fgo:ScreenFlowStart}}
\subsubsection*{Class: \texttt{fgo:Trigger}}

@@

\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:hasIdActionTo}}{subs:hasIdActionTo}, \htmlref{\texttt{fgo:hasIdBBFrom}}{subs:hasIdBBFrom}, \htmlref{\texttt{fgo:hasIdBBTo}}{subs:hasIdBBTo}, \htmlref{\texttt{fgo:hasNameFrom}}{subs:hasNameFrom} \\ \hline

@@

\subsubsection*{Class: \texttt{fgo:WithConditions}}

@@

\textcolor{white}{\textbf{unionOf}} & \htmlref{\texttt{fgo:WithPostConditions}}{subs:WithPostConditions}, \htmlref{\texttt{fgo:WithPreConditions}}{subs:WithPreConditions} \\ \hline

@@

\subsubsection*{Class: \texttt{fgo:WithPostConditions}}

@@

\textcolor{white}{\textbf{label}} & With-post-condition \\ \hline
\textcolor{white}{\textbf{description}} & Those kinds of resources which can have post-conditions. \\ \hline
\textcolor{white}{\textbf{unionOf}} & \htmlref{\texttt{fgo:Screen}}{subs:Screen}, \htmlref{\texttt{fgo:ScreenComponent}}{subs:ScreenComponent}, \htmlref{\texttt{fgo:ScreenFlow}}{subs:ScreenFlow} \\ \hline

@@

\subsubsection*{Class: \texttt{fgo:WithPreConditions}}

@@

\textcolor{white}{\textbf{label}} & With-pre-condition \\ \hline
\textcolor{white}{\textbf{description}} & Those kinds of resources which can have pre-conditions. \\ \hline
\textcolor{white}{\textbf{unionOf}} & \htmlref{\texttt{fgo:Action}}{subs:Action}, \htmlref{\texttt{fgo:Screen}}{subs:Screen}, \htmlref{\texttt{fgo:ScreenFlow}}{subs:ScreenFlow} \\ \hline
